Reducing bias in secondary data analysis via an Explore and Confirm Analysis Workflow (ECAW): A proposal and survey of observational researchers

### 2023-04-28 manuscript/supplementary_materials.Rmd
changed faulty figure numbers

```{r numStudiesPlot, fig.align="center", out.width="100%", fig.width=6, fig.height=3.2, fig.path='figs/', dev=c('png', 'pdf')}
# Create text for missing responses
n_studies_missing_text <- 
  processed %>% 
  filter(is.na(n_studies)) %>% 
  summarise(
    n = n(),
    missing_text = paste0("missing = ", n)
  ) %>% 
  pull(missing_text)

@@

@@

```{=latex}
{\smaller[1]
\begin{singlespace}
```
(ref:concernedPlotCaption) __Figure C1. Responses to survey question about number of relevant publications__
```{=latex}
\end{singlespace}
}
```

>>>>

```{r numStudiesPlot, fig.align="center", fig.cap="(ref:numStudiesPlotCaption)", out.width="100%", fig.width=6, fig.height=3.2, fig.path='figs/', dev=c('png', 'pdf')}
# Create text for missing responses
n_studies_missing_text <- 
  processed %>% 
  filter(is.na(n_studies)) %>% 
  summarise(
    n = n(),
    missing_text = paste0("missing = ", n)
  ) %>% 
  pull(missing_text)

@@

```{=latex}
{\smaller[1]
\begin{singlespace}
```
(ref:numStudiesPlotCaption) __Figure C1.__
```{=latex}
\end{singlespace}
}
```

@@

```{=latex}
{\smaller[1]
\begin{singlespace}
```
(ref:concernedPlotCaption) __Figure C2. Responses to survey question about number of relevant publications__
```{=latex}
\end{singlespace}
}
```
